---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mbrdt

<!-- badges: start -->
[![R-CMD-check](https://github.com/bj0909/mbrdt/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/bj0909/mbrdt/actions/workflows/R-CMD-check.yaml)
[![Travis build status](https://travis-ci.com/bj0909/mbrdt.svg?branch=master)](https://travis-ci.com/bj0909/mbrdt)
<!-- badges: end -->

The goal of mbrdt is to provide tools for designing multistage binomial reliability demonstration tests (MRDTs). 
    It allows researchers and practitioners to simulate and optimize the costs of 
MBRDT designs, considering the multi-stage acceptance uncertainties and the potential 
subsequent costs of RDT, such as reliability growth costs and warranty service costs.

## Installation

You can install the development version of mbrdt like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(mbrdt)

## basic example code
```


